---
title: "Untitled"
author: "Zidani"
date: "7/1/2021"
output: html_document
---

```{r}

my_data <- PlantGrowth
my_data



```
```{r}
 #Show a random sample
set.seed(1234)
dplyr::sample_n(my_data, 10)

```

```{r}
# Show the levels
levels(my_data$group)
```
```{r}
# visualise data
# Plot weight by group and color by group
library("ggpubr")
ggboxplot(my_data, x = "group", y = "weight", 
          color = "group", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("ctrl", "trt1", "trt2"),
          ylab = "Weight", xlab = "Treatment")

```


Computing a one-way ANOVA test

We want to know if there is any significant difference between the average weights of plants in the 3 experimental conditions.

```{r}
# Compute the analysis of variance
res.aov <- aov(weight ~ group, data = my_data)
res.aov
```

```{r}
# Summary of the analysis
summary(res.aov)
```

Interpreting the result of one-way ANOVA tests
```{r}
As the p-value is less than the significance level 0.05, we can conclude that there are significant differences between the groups highlighted with “*" in the model summary.
```

Multiple pairwise-comparison between the means of groups(This is to determine if the mean difference between specific pairs of group are statistically significant.)
we are using Tukey multiple pairwise-comparisons
```{r}

TukeyHSD(res.aov)

```
diff: difference between means of the two groups
lwr, upr: the lower and the upper end point of the confidence interval at 95% (default)
p adj: p-value after adjustment for the multiple comparisons.

Interpreting the Results
It can be seen from the output, that only the difference between trt2 and trt1 is significant with an adjusted p-value of 0.012.
```{r}

```

